### 2017-01-22 thesis/latex/thesis.tex
Add work on rate constant fitting and add sample histograms to results.

@@

@@

%% \begin{figure}[h!]
%%   \centering
%%   \begin{minipage}[b]{0.49\textwidth}
%%     \includegraphics[width=\textwidth]{../../figures/OB_Average_PE.pdf}
%%     \caption{Onebound PE vs time.}
%%   \end{minipage}
%%   \begin{minipage}[b]{0.49\textwidth}
%%     \includegraphics[width=\textwidth]{../../figures/BB_Average_PE.pdf}
%%     \caption{Bothbound PE vs time.}
%%   \end{minipage}
%%   \label{equipartition_agreement}
%% \end{figure}

\textbf{Possibly do mutations on motion equations to show that tests are no longer behaved}
\subsubsection{Finding proper $dt$}

\subsubsection{Equipartition theorem obeyed}
%% \begin{figure}[h!]
%%   \centering
%%   \begin{minipage}[b]{0.49\textwidth}
%%     \includegraphics[width=\textwidth]{../../figures/OB_Average_PE.pdf}
%%     \caption{Onebound PE vs time.}
%%   \end{minipage}
%%   \begin{minipage}[b]{0.49\textwidth}
%%     \includegraphics[width=\textwidth]{../../figures/BB_Average_PE.pdf}
%%     \caption{Bothbound PE vs time.}
%%   \end{minipage}
%%   \label{fig:equipartition_agreement}
%% \end{figure}

@@

What's more, using exact literature values for each parameter does not necessarily create the simulation most similar to \textit{in vivo} dynein. Defects and simplifications in the model may cause slightly less physical values for individual parameters to lead to a more physical simulation. For this reason, fitting model parameters to experiment is necessary. This process is chronicled below.

\begin{figure}[h]
  \centering
  \begin{tabular}{| l | l | l | l | l | l | l | l | l |}
    \hline
    & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7 & Redwine & Kon & Burgess \\\hline
    $L_s$ & 12nm & & & 21.0nm & 22.1nm & & & \\ \hline
    $L_t$ &  7nm & & & & 11.15nm & & & \\ \hline
    $R_b$ &  & & & 1.57nm & 1.45nm & & & \\ \hline
    $R_m$ &  7nm & & & 7.36nm & 6.3nm & & & \\ \hline
    $R_t$ &  & & & & 2.16nm & & & \\ \hline
    $\theta_{m}^{Pre}$ & 250$^{\circ}$ & & 171$^{\circ}$ & & & & & 160\\ \hline
    $\theta_{m}^{Post}$ & 330$^{\circ}$ & & 137.5$^{\circ}$ & & & & & 136\\ \hline
    $\theta_{b}$ & 56$^{\circ}$ & & 63.5$^{\circ}$ & & & & & \\ \hline
    $\theta_{t}$ & 0$^{\circ}$ & & & & & & & \\ \hline
    $k_{ub}$ & $180 s^{-1,a}$ & & & & & & $90.2 \pm 4.5$& \\ \hline
    $k_b$ & $5000 s^{-1,b}$ & & & & & & & \\ \hline
    $\Delta G_{bind, bb}$ & & & & & & -71 kJ/mol & & \\ \hline
    $\Delta G_{bind, ob}$ & & & & & & -37 kJ/mol & & \\ \hline
    $c_t$ & & & & & & & & \\ \hline
    $c_m$ & & & & & & & & \\ \hline
    $c_b$ & & & & & & 140 kJ/mol & & \\ \hline
  \end{tabular}
  \caption{Table of literature values for various free parameters in dynein model.}
  \label{parameter-table}
\end{figure}

\subsubsection{Fitting rate constants}
Rate constants $k_b$ and $k_{ub}$ govern the probability of transitioning from onebound to bothbound and vice-versa, respectively. As shown in Section \ref{sec:transitioning-states}, these values can be calculated using the Arrhenius equation:

\begin{equation*}
  k_b = Ae^{\frac{-\Delta G}{k_BT}} = Ae^{\frac{-\Delta G_{conf}}{k_BT}}e^{\frac{-\Delta G_{bind}}{k_BT}}
\end{equation*}

One issue is that $\Delta G_{conf}$ is based on the current conformation of the model, whereas $k_b$ is a macroscopic parameter representative of all conformations of dynein. This is resolved by replacing $\Delta G_{conf}$ with $\left<\Delta G_{conf}\right>$, the expectation value of energy change in going from onebound to bothbound states. This expected energy, by the equipartition theorem, is $2k_BT$ for onebound and $k_BT$ for bothbound. Conversely $\Delta G_{bind}$ is a constant. Thus the rates can be rewritten:

\begin{equation*}
  k_b = Ae^{\frac{-\Delta G_{conf}}{k_BT}}e^{\frac{-k_BT\left(1-2\right)}{k_BT}} = \frac{A_b}{e}
\end{equation*}

where $A_b = Ae^{\frac{-\Delta G_{bind}}{k_BT}}$. Thus literature values on MT binding rate can be used in our model to calculate $A_b$.

\textbf{now explain what literature values were used, and why those are reasonable guesses.}

\subsubsection{Fitting spring constants}
\subsubsection{Finding parameters from PyMol}
\subsubsection{Finding values from literature}
\subsubsection{Final parameter guess table}
\subsubsection{Finding the right timestep}

@@

------------------------------------------

@@

\subsection{Histograms}
\subsubsection{Step length histograms}
\subsubsection{Step time histograms}
\subsection{Other ways to represent data?}

>>>>

\textit{Add figure somewhere of this cycle superimposed with markings of what states are considered onebound and bothbound}\\

@@

\begin{figure}[h!]
  \centering
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../../figures/OB_Average_PE.pdf}
    \caption{Average domain PE of onebound model converging to $\frac12 k_BT$ energy over time.}
  \end{minipage}
  \hspace{.2cm}
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../../figures/BB_Average_PE.pdf}
    \caption{Total domain PE of bothbound model converging to $\frac12 k_BT$ energy over time.}
  \end{minipage}
  \label{fig:equipartition_agreement}
\end{figure}

@@

\textbf{Possibly do mutations on motion equations to show that tests are no longer behaved}

@@

What's more, using exact literature values for each parameter does not necessarily create the simulation most similar to \textit{in vivo} dynein. Defects and simplifications in the model may cause slightly less physical values for individual parameters to lead to a more physical simulation. For this reason, fitting model parameters to experiment is necessary. This process is chronicled below. Table \ref{table:parameter-table} concisely lists literature values for various parameters.

\begin{figure}[h]
  \centering
  \begin{tabular}{| l | l | l | l | l | l | l | l | l |}
    \hline
    & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7 & Redwine & Kon & Burgess \\\hline
    $L_s$ & 12nm & & & 21.0nm & 22.1nm & & & \\ \hline
    $L_t$ &  7nm & & & & 11.15nm & & & \\ \hline
    $R_b$ &  & & & 1.57nm & 1.45nm & & & \\ \hline
    $R_m$ &  7nm & & & 7.36nm & 6.3nm & & & \\ \hline
    $R_t$ &  & & & & 2.16nm & & & \\ \hline
    $\theta_{m}^{Pre}$ & 250$^{\circ}$ & & 171$^{\circ}$ & & & & & 160\\ \hline
    $\theta_{m}^{Post}$ & 330$^{\circ}$ & & 137.5$^{\circ}$ & & & & & 136\\ \hline
    $\theta_{b}$ & 56$^{\circ}$ & & 63.5$^{\circ}$ & & & & & \\ \hline
    $\theta_{t}$ & 0$^{\circ}$ & & & & & & & \\ \hline
    $k_{ub}$ & $180 s^{-1,a}$ & & & & & & $90.2 \pm 4.5$& \\ \hline
    $k_b$ & $5000 s^{-1,b}$ & & & & & & & \\ \hline
    $c_t$ & & & & & & & & \\ \hline
    $c_m$ & & & & & & & & \\ \hline
    $c_b$ & & & & & & 140 kJ/mol & & \\ \hline
  \end{tabular}
  \caption{Table of literature values for various free parameters in dynein model.}
  \label{table:parameter-table}
\end{figure}

In addition, the physical conditions the simulations were run at are shown in Table \ref{table:simulation-conditions}. These conditions are meant to reflect the conditions found inside a typical cell. \textbf{of what species?}\\

\begin{figure}[h]
  \centering
  \begin{tabular}{| l | l |}
    \hline
    T & [ATP] \\ \hline
    310.15 K & $1.54*10^{-3}$ M \cite{cellular-atp}\\ \hline
  \end{tabular}
  \caption{Table of physical constants used in simulation.}
  \label{table:parameter-table}
\end{figure}

\subsubsection{Fitting rate constants}
\paragraph{Converting experimental rates to preexponential factors $A_b$ and $A_{ub}$}
Rate constants $k_b$ and $k_{ub}$ govern the probability of transitioning from onebound to bothbound and vice-versa, respectively. One issue is that when these parameters are measured experimentally, the values represent the average rate for an ensemble of dynein in many different conformations. In contrast, the rates the model uses represent the probability of unbinding of a specific conformation. Thus, it is necessary to find a way to convert between experimental rates $k_b^{exp}$ and $k_{ub}^{exp}$ and conformation-specific rates $k_b$ and $k_{ub}$. As shown in Section \ref{sec:transitioning-states}, rates can be expressed using the Arrhenius equation:

\begin{align*}
  k_b &= A_b'e^{\frac{-\Delta G_{bind}}{k_BT}} = A_b'e^{\frac{-\Delta G_{conf}^{ob\rightarrow bb}}{k_BT}}e^{\frac{-\Delta G_{bind}}{k_BT}} = A_be^{\frac{-\Delta G_{conf}^{ob\rightarrow bb}}{k_BT}}\\
  k_{ub} &= A_{ub}'e^{\frac{-\Delta G_{unbind}}{k_BT}} = A_{ub}'e^{\frac{-\Delta G_{conf}^{bb\rightarrow ob}}{k_BT}}e^{\frac{\Delta G_{bind}}{k_BT}} = A_{ub}e^{\frac{-\Delta G_{conf}^{bb\rightarrow ob}}{k_BT}}
\end{align*}

where the constant Boltzmann factor for binding energy are hidden inside the unprimed preexponential factors. The experimental values are calculated the same way, with the free energy changes replaced with expectation values. Since by the equipartition theorem $\left<G_{conf}^{ob}\right> = 2k_BT$ and $\left<G_{conf}^{bb}\right> = k_BT$, the equations can be simplified:

\begin{align*}
  k_b^{exp} &= A_be^{\frac{-\left(2k_BT - k_BT\right)}{k_BT}} = \frac{A_b}{e}\\
  k_{ub}^{exp} &= A_{ub}e^{\frac{-\left(k_BT-2k_BT\right)}{k_BT}} = A_{ub}e
\end{align*}

Thus experimental rates can be converted easily into the model parameters $A_b$ and $A_{ub}$.

\paragraph{Literature values for experimental binding rates}
Sarlah \textit{et. al.} \cite{sarlahmodel} perform a similar simulation of dynein and provide the reaction rates shown in Figure \ref{fig:sarlah-rate-table}.

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{../../figures/SarlahParameterTable.png}
  \caption{Kinetic rates used in Sarlah \textit{et. al.}'s model \cite{sarlahmodel}.}
  \label{fig:sarlah-rate-table}
\end{figure}

The assumption of this project is that many of the states in this table can be combined into a single state without loss of predictive power of dynein behavior. Specifically, the assumption is that ejecting phosphate, conducting the powerstroke, releasing ADP, binding ATP and dissociating from the microtubule and all occur during the bothbound state, and hydrolyzing ATP, conducting the prestroke and rebinding the MT occur during onebound. These states are roughly grouped as MT-bound and MT-unbound states in the Cianfrocco mechanochemical cycle \cite{cianfroccoreview}.\\

The rate-limiting transitions in the Cianfrocco model are used as the guess $k_b$ and $k_{ub}$ values. That means that, since ATP hydrolysis has the slowest rate constant in onebound and MT release has the slowest rate in bothbound, $k_b^{exp} = 180 s^{-1}$ and $k_{ub} = 460 s^{-1}$ serve as good initial guesses.\\

\paragraph{Fitting rate constants by simulation}
\textit{Add in a plot of the binding rate fitting search}

\subsubsection{Fitting spring constants}
\paragraph{Using $\Delta G_{bind}$ to guess $c_b$}
\paragraph{Using $\Theta_m$ standard deviation to guess $c_m$}
\paragraph{Fitting rate constants by simulation}

\subsubsection{Finding parameters from PyMol}

\subsubsection{Finding the right timestep}

@@

@@

\subsection{Histograms}

\begin{figure}[h!]
  \centering
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../../figures/length_histogram_sample.pdf}
    \caption{Histogram of simulated stepping lengths using ideal dynein parameters. Todo: superimpose Weihong's histogram of the same.}
  \end{minipage}
  \hspace{.1cm}
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../../figures/time_histogram_sample.pdf}
    \caption{Histogram of simulated stepping times using ideal dynein parameters. Todo: superimpose Weihong's histogram of the same.}
  \end{minipage}
  \label{fig:equipartition_agreement}
\end{figure}

\subsection{Other ways to represent data?}
